---
title: "AFRICA PROJECT - ECONOMIC GROWTH AND DEVELOPMENT"
author: "Braeden Templin"
date: "March 26, 2026"
---

```{r}
library(readr)
library(dplyr)
library(janitor)
library(readxl)
library(ggplot2)
library(flextable)
```

# Sub-Saharan Comparison and Modeling

All Countries include:\

- Ghana
- Nigeria
- Côte d'Ivoire
- Senegal
- Cameroon
- Togo
- Sierra Leone
- Liberia

(The US has been added for comparison)

The goal of this is to help visualize comparisons and create actual Solow growth models we can see.\

## Heritage Index of Economic Freedom

```{r}
# Read in Dataset and Clean
heritage_index <- read_csv("heritage-index-of-economic-freedom-2026-03-25_1950.csv")
heritage_index <- clean_names(heritage_index)

# Subsetted Dataframe with Relevant Countries
heritage_2025 <- heritage_index %>% 
  filter(index_year == 2026) %>% 
    filter(country %in% c('Ghana', 
                          'Nigeria',
                          "Côte d'Ivoire",
                          'Senegal',
                          'Cameroon',
                          'Togo',
                          'Sierra Leone',
                          'Liberia',
                          'United States'))
```

Below are bar graphs that compare each Economic Index given the list of counties\

```{r}

# ======== Overall Score ========

heritage_2025 %>%
  mutate(overall_score = as.numeric(overall_score)) %>% 
  arrange(overall_score) %>%
  ggplot(aes(x = overall_score, y = reorder(country, overall_score))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(overall_score, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  
  labs(
    title = "Overall Score by Country",
    x = "Overall Score",
    y = "Country"
  ) +
  
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Property Rights ========

heritage_2025 %>%
  mutate(property_rights = as.numeric(property_rights)) %>% 
  arrange(property_rights) %>%   # sort for clean visual
  ggplot(aes(x = property_rights, y = reorder(country, property_rights))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(property_rights, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "property_rights by Country",
    x = "property_rights",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Government Integrity ========

heritage_2025 %>%
  mutate(government_integrity = as.numeric(government_integrity)) %>% 
  arrange(government_integrity) %>%   # sort for clean visual
  ggplot(aes(x = government_integrity, y = reorder(country, government_integrity))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(government_integrity, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "government_integrity by Country",
    x = "government_integrity",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Judicial Effectiveness ========

heritage_2025 %>%
  mutate(judicial_effectiveness = as.numeric(judicial_effectiveness)) %>% 
  arrange(judicial_effectiveness) %>%   # sort for clean visual
  ggplot(aes(x = judicial_effectiveness, y = reorder(country, judicial_effectiveness))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(judicial_effectiveness, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "judicial_effectiveness by Country",
    x = "judicial_effectiveness",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Tax Burdens ========

heritage_2025 %>%
  mutate(tax_burden = as.numeric(tax_burden)) %>% 
  arrange(tax_burden) %>%   # sort for clean visual
  ggplot(aes(x = tax_burden, y = reorder(country, tax_burden))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(tax_burden, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "tax_burden by Country",
    x = "tax_burden",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Government Spending ========

heritage_2025 %>%
  mutate(government_spending = as.numeric(government_spending)) %>% 
  arrange(government_spending) %>%   # sort for clean visual
  ggplot(aes(x = government_spending, y = reorder(country, government_spending))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(government_spending, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "government_spending by Country",
    x = "government_spending",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Fiscal Health ========

heritage_2025 %>%
  mutate(fiscal_health = as.numeric(fiscal_health)) %>% 
  arrange(fiscal_health) %>%   # sort for clean visual
  ggplot(aes(x = fiscal_health, y = reorder(country, fiscal_health))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(fiscal_health, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "fiscal_health by Country",
    x = "fiscal_health",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Business Freedom ========

heritage_2025 %>%
  mutate(business_freedom = as.numeric(business_freedom)) %>% 
  arrange(business_freedom) %>%   # sort for clean visual
  ggplot(aes(x = business_freedom, y = reorder(country, business_freedom))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(business_freedom, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "business_freedom by Country",
    x = "business_freedom",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Labor Freedom ========

heritage_2025 %>%
  mutate(labor_freedom = as.numeric(labor_freedom)) %>% 
  arrange(labor_freedom) %>%   # sort for clean visual
  ggplot(aes(x = labor_freedom, y = reorder(country, labor_freedom))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(labor_freedom, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "labor_freedom by Country",
    x = "labor_freedom",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Monetary Freedom ========

heritage_2025 %>%
  mutate(monetary_freedom = as.numeric(monetary_freedom)) %>% 
  arrange(monetary_freedom) %>%   # sort for clean visual
  ggplot(aes(x = monetary_freedom, y = reorder(country, monetary_freedom))) +
  geom_col(fill = "#7FE8D7") +

  geom_text(aes(label = round(monetary_freedom, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "monetary_freedom by Country",
    x = "monetary_freedom",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Trade Freedom ========

heritage_2025 %>%
  mutate(trade_freedom = as.numeric(trade_freedom)) %>% 
  arrange(trade_freedom) %>%   # sort for clean visual
  ggplot(aes(x = trade_freedom, y = reorder(country, trade_freedom))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(trade_freedom, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "trade_freedom by Country",
    x = "trade_freedom",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Investment Freedom ========

heritage_2025 %>%
  mutate(investment_freedom = as.numeric(investment_freedom)) %>% 
  arrange(investment_freedom) %>%   # sort for clean visual
  ggplot(aes(x = investment_freedom, y = reorder(country, investment_freedom))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(investment_freedom, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "investment_freedom by Country",
    x = "investment_freedom",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Financial Freedom ========

heritage_2025 %>%
  mutate(financial_freedom = as.numeric(financial_freedom)) %>% 
  arrange(financial_freedom) %>%   # sort for clean visual
  ggplot(aes(x = financial_freedom, y = reorder(country, financial_freedom))) +
  geom_col(fill = "#7FE8D7") +
  
  geom_text(aes(label = round(financial_freedom, 1)), 
            hjust = -0.1, 
            color = "#7FE8D7",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    title = "financial_freedom by Country",
    x = "financial_freedom",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

```

## Business Ready - The World Bank

These reflect the overall index scores from the business ready dataset. Not included are the specific pillars in each of the categories, but the data is stored so I can create graphs if that would be meaningful for analysis or comparison.\

```{r}

# ======== Pillar Score ========

b_ready_index <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "00_B-READY_Pillar_Score")
b_ready_index <- b_ready_index %>%
  select(-`Economy Code`) %>% 
  filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Business Entry ========

b_ready_business_entry <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "01_Business_Entry", skip = 3)
b_ready_business_entry <- b_ready_business_entry %>%
 select(Economy, `Business Entry Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>%
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Business Location ========

b_ready_business_location <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "02_Business_Location", skip = 3)
b_ready_business_location <- b_ready_business_location %>% 
 select(Economy, `Business Location Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Utility Services ========

b_ready_utility_services <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "03_Utility_Services", skip = 3)
b_ready_utility_services <- b_ready_utility_services %>% 
 select(Economy, `Utility Services Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Labor ========

b_ready_labor <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "04_Labor", skip = 3)
b_ready_labor <- b_ready_labor %>% 
 select(Economy, `Labor Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Financial Services ========

b_ready_financial_services <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "05_Financial_Services", skip = 3)
b_ready_financial_services <- b_ready_financial_services %>% 
 select(Economy, `Financial Services Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== International Trade ========

b_ready_international_trade <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "06_International_Trade", skip = 3)
b_ready_international_trade <- b_ready_international_trade %>% 
 select(Economy, `International Trade Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Taxation ========

b_ready_taxation <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "07_Taxation", skip = 3)
b_ready_taxation <- b_ready_taxation %>% 
 select(Economy, `Taxation Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Dispute Resolution ========

b_ready_dispute_resolution <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "08_Dispute_Resolution", skip = 3)
b_ready_dispute_resolution <- b_ready_dispute_resolution %>% 
 select(Economy, `Dispute Resolution Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Market Competition ========

b_ready_market_competition <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "09_Market_Competition", skip = 3)
b_ready_market_competition <- b_ready_market_competition %>% 
 select(Economy, `Market Competition Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

# ======== Business Insolvency ========

b_ready_business_insolvency <- read_excel("01_B-READY-2025-PILLAR-TOPIC-SCORES.xlsx", sheet = "10_Business_Insolvency", skip = 3)
b_ready_business_insolvency <- b_ready_business_insolvency %>% 
 select(Economy, `Business Insolvency Overall`, `Pillar 1 Overall`, `Pillar 2 Overall`, `Pillar 3 Overall`) %>% 
 filter(Economy %in% c('Ghana', 
                    'Nigeria',
                    "Côte d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States'))

```

```{r}
# ======== Business Entry ========

b_ready_business_entry %>%
  ggplot(aes(
    x = `Business Entry Overall`,
    y = reorder(Economy, `Business Entry Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Business Entry Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Business Entry Overall by Country",
    x = "Business Entry Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Business Location ========

b_ready_business_location %>%
  ggplot(aes(
    x = `Business Location Overall`,
    y = reorder(Economy, `Business Location Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Business Location Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Business Location Overall by Country",
    x = "Business Location Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Utility Services ========

b_ready_utility_services %>%
  ggplot(aes(
    x = `Utility Services Overall`,
    y = reorder(Economy, `Utility Services Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Utility Services Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Utility Services Overall by Country",
    x = "Utility_Services Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Labor ========

b_ready_labor %>%
  ggplot(aes(
    x = `Labor Overall`,
    y = reorder(Economy, `Labor Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Labor Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Labor Overall by Country",
    x = "Labor Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Financial Services ========

b_ready_financial_services %>%
  ggplot(aes(
    x = `Financial Services Overall`,
    y = reorder(Economy, `Financial Services Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Financial Services Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Financial Services Overall by Country",
    x = "Financial Services Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== International Trade ========

b_ready_international_trade %>%
  ggplot(aes(
    x = `International Trade Overall`,
    y = reorder(Economy, `International Trade Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`International Trade Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "International Trade Overall by Country",
    x = "International Trade Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Taxation ========

b_ready_taxation %>%
  ggplot(aes(
    x = `Taxation Overall`,
    y = reorder(Economy, `Taxation Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Taxation Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Taxation Overall by Country",
    x = "Taxation Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Dispute Resolution ========

b_ready_dispute_resolution %>%
  ggplot(aes(
    x = `Dispute Resolution Overall`,
    y = reorder(Economy, `Dispute Resolution Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Dispute Resolution Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Dispute Resolution Overall by Country",
    x = "Dispute Resolution Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Market Competition ========

b_ready_market_competition %>%
  ggplot(aes(
    x = `Market Competition Overall`,
    y = reorder(Economy, `Market Competition Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Market Competition Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Market Competition Overall by Country",
    x = "Market Competition Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# ======== Business Insolvency ========

b_ready_business_insolvency %>%
  ggplot(aes(
    x = `Business Insolvency Overall`,
    y = reorder(Economy, `Business Insolvency Overall`)
  )) +
  geom_col(fill = "#FF8C7F") +
  
  geom_text(aes(label = round(`Business Insolvency Overall`, 1)),
            hjust = -0.1,
            color = "#FF8C7F",
            size = 4) +
  
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 10)) +
  labs(
    title = "Business Insolvency Overall by Country",
    x = "Business Insolvency Overall",
    y = "Country"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

```

## Corruptions Perception Index - Transperancy International

Below is a bar graph which each nations corruption index score followed by their rank in parenthesis.\

```{r}
# Import Dataframe from Corruption Index
corruption_index <- read_excel("CPI2025_Results.xlsx", skip = 2)
corruption_index <- corruption_index %>% 
  select(`Country / Territory`, `CPI 2025 score`, Rank) %>% 
  mutate(Country = `Country / Territory`,
         Score = `CPI 2025 score`) %>%
  filter(Country %in% c('Ghana', 
                    'Nigeria',
                    "Cote d'Ivoire",
                    'Senegal',
                    'Cameroon',
                    'Togo',
                    'Sierra Leone',
                    'Liberia',
                    'United States of America')) %>% 
  select(-`Country / Territory`, -`CPI 2025 score`) %>% 
  mutate(Country = ifelse(Country == "United States of America", "United States", Country),
         Country = ifelse(Country == "Cote d'Ivoire", "Côte d'Ivoire", Country))

```

```{r}
# Graph for Corruption Index
corruption_index %>%
  ggplot(aes(
    x = Score,
    y = reorder(Country, Score)
  )) +
  geom_col(fill = "#7B83EB") +
  
  # ✅ Label: Score (Rank)
  geom_text(aes(label = paste0(round(Score, 1), " (", Rank, ")")),
            hjust = -0.1,
            color = "#7B83EB",
            size = 4) +
  
  scale_x_continuous(breaks = seq(0, 100, 10)) +
  coord_cartesian(xlim = c(0, 105)) +
  
  labs(
    title = "Corruption Perceptions Index (2025)",
    x = "Score",
    y = "Country"
  ) +
  
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

## Solow Growth Models - Penn World Table & World Bank

```{r}

# ======== World Bank (Savings) ========

savings_rate_as_pct_gdp <- read_excel("API_NY.GNS.ICTR.ZS_DS2_en_excel_v2_330.xls", skip = 2)
savings_rate_as_pct_gdp <- clean_names(savings_rate_as_pct_gdp)

savings_rate_as_pct_gdp <- savings_rate_as_pct_gdp %>% 
  select(country_name, x2023) %>%
  filter(country_name %in% c('Ghana', 
                             'Nigeria',
                             "Cote d'Ivoire",
                             'Senegal',
                             'Cameroon',
                             'Togo',
                             'Sierra Leone',
                             'Liberia',
                             'United States')) 

# Parameters to Adjust (Must be in % format)
Nigeria_Savings_Rate = median(savings_rate_as_pct_gdp$x2023, na.rm = TRUE)
Liberia_Savings_Rate = median(savings_rate_as_pct_gdp$x2023, na.rm = TRUE)
Togo_Savings_Rate    = (16.498484 * 17.799610 * 19.5264093)^(1/3)

savings_rate_as_pct_gdp <- savings_rate_as_pct_gdp %>% 
  mutate(x2023 = ifelse(country_name == "Togo", Togo_Savings_Rate, x2023),
         x2023 = ifelse(country_name == "Nigeria", Nigeria_Savings_Rate, x2023),
         x2023 = ifelse(country_name == "Liberia", Liberia_Savings_Rate, x2023),
         country_name = ifelse(country_name == "Cote d'Ivoire", "Côte d'Ivoire", country_name),
         x2023 = x2023 / 100) %>% 
  rename(s = x2023)

# ======== Penn World Table ========

pwt_base <- read_excel("pwt110.xlsx", sheet = "Data")
pwt_base <- clean_names(pwt_base)

pwt_base <- pwt_base %>% 
  select(country, year, rgdpo, rnna, emp, labsh) %>%
  filter(country %in% c("Ghana", 
                        "Nigeria", 
                        "Côte d'Ivoire",
                        "Senegal", 
                        "Cameroon", 
                        "Togo", 
                        "Sierra Leone", 
                        "Liberia", 
                        "United States")) %>% 
  filter(year >= 2022)

# Parameters to Adjust (alpha)
Ghana_Labsh   = median(pwt_base$labsh, na.rm = TRUE)
Liberia_Labsh = median(pwt_base$labsh, na.rm = TRUE)

pwt_base <- pwt_base %>%
  mutate(labsh = ifelse(country == "Ghana", Ghana_Labsh, labsh),
         labsh = ifelse(country == "Liberia", Liberia_Labsh, labsh))

pwt_base <- pwt_base %>% 
  mutate(y = rgdpo / emp,
         k = rnna / emp,
         n = ((emp / lag(emp)) -1),
         d = 0.05,
         a = (1 - labsh),
         L = emp,
         K = rnna,
         Y = rgdpo,
         A = Y / (K^a * L^(1 - a)))

# ======== Full Solow Dataset ========

pwt_solow <- pwt_base %>% 
  filter(year == 2023) %>% 
  select(country, Y, A, K, L, y, k, a, n, d)

pwt_solow <- pwt_solow %>%
  left_join(
    savings_rate_as_pct_gdp %>% select(country_name, s),
    by = c("country" = "country_name"))

# ======== Full Solow Flextable ========

library(dplyr)
library(flextable)

pwt_solow_ft <- pwt_solow %>%
  mutate(
    Y = round(Y, 2),
    A = round(A, 2),
    K = round(K, 2),
    L = round(L, 2),
    y = round(y, 2),
    k = round(k, 2),
    a = round(a, 3),
    n = round(n, 3),
    d = round(d, 3),
    s = round(s, 3)
  ) %>%
  rename(
    Country = country,
    `Output (Y)` = Y,
    `Technology (A)` = A,
    `Capital (K)` = K,
    `Labor (L)` = L,
    `Output per Worker (y)` = y,
    `Capital per Worker (k)` = k,
    `Capital Share (a)` = a,
    `Labor Growth (n)` = n,
    `Depreciation (d)` = d,
    `Savings Rate (s)` = s
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Solow Model Parameters by Country (2023)",
    colwidths = 11
  ) %>%
  theme_box() %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

pwt_solow_ft

```

All data was taken from the Penn World Table (https://www.rug.nl/ggdc/productivity/pwt/). The World Bank was used for the savings rate which was taken as Gross Savings % GDP (https://data.worldbank.org/indicator/NY.GNS.ICTR.ZS). The most recent available data is from 2023. The depreciate rate I found was not given anywhere, so we are to assume 5%.\

Important Note: Savings Rate is missing for Togo, Nigeria, and Liberia. To correct this, the last three known values for Togo are a geometric average (2017-2019) to calculate the current value. For Nigeria and Liberia, the median from all the countries in our report was taken. The same thing is done for Ghana and Liberia in finding alpha or capital share of income.\

Import Note: All values are able to be adjusted, so if you found a different number I can put it into the model.\

Consideration: I am not sure the savings rate is correct given the actual point on the graph, could be something to discuss or look into.\

### Côte d'Ivoire

```{r}

# ======== Côte d'Ivoire ========

CIV_solow <- pwt_solow %>%
  filter(country == "Côte d'Ivoire")

# Input Variables

CIV_a         <- CIV_solow$a[1]
CIV_s         <- CIV_solow$s[1]
CIV_n         <- CIV_solow$n[1]
CIV_d         <- CIV_solow$d[1]
CIV_A         <- CIV_solow$A[1]
CIV_k_current <- CIV_solow$k[1]
CIV_y_current <- CIV_solow$y[1]

# Steady State

CIV_k_star <- ((CIV_s * CIV_A) / (CIV_n + CIV_d))^(1 / (1 - CIV_a))
CIV_y_star <- CIV_A * CIV_k_star^CIV_a
CIV_sfk_star <- CIV_s * CIV_y_star

# Graph

CIV_solow_df <- data.frame(
  k = seq(0, CIV_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = CIV_A * k^CIV_a,
    sfk = CIV_s * y,
    break_even = (CIV_n + CIV_d) * k
  )

CIV_last_point <- CIV_solow_df %>%
  slice_tail(n = 1)

ggplot(CIV_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = CIV_k_star, linetype = "dotted") +
  geom_point(aes(x = CIV_k_star, y = CIV_sfk_star), size = 2) +
  geom_point(aes(x = CIV_k_current, y = CIV_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = CIV_last_point$k,
    y = CIV_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = CIV_last_point$k,
    y = CIV_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = CIV_last_point$k,
    y = CIV_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - Côte d'Ivoire",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(CIV_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

CIV_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    CIV_k_star,
    CIV_k_star,
    CIV_k_current
  ),
  y_coordinate = c(
    CIV_sfk_star,
    CIV_y_star,
    CIV_y_current
  )
)

CIV_ss_points_ft <- CIV_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Côte d'Ivoire Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

CIV_ss_points_ft
```

### Cameroon

```{r}

# ======== Cameroon ========

CMR_solow <- pwt_solow %>%
  filter(country == "Cameroon")

# Input Variables

CMR_a         <- CMR_solow$a[1]
CMR_s         <- CMR_solow$s[1]
CMR_n         <- CMR_solow$n[1]
CMR_d         <- CMR_solow$d[1]
CMR_A         <- CMR_solow$A[1]
CMR_k_current <- CMR_solow$k[1]
CMR_y_current <- CMR_solow$y[1]

# Steady State

CMR_k_star <- ((CMR_s * CMR_A) / (CMR_n + CMR_d))^(1 / (1 - CMR_a))
CMR_y_star <- CMR_A * CMR_k_star^CMR_a
CMR_sfk_star <- CMR_s * CMR_y_star

# Graph

CMR_solow_df <- data.frame(
  k = seq(0, CMR_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = CMR_A * k^CMR_a,
    sfk = CMR_s * y,
    break_even = (CMR_n + CMR_d) * k
  )

CMR_last_point <- CMR_solow_df %>%
  slice_tail(n = 1)

ggplot(CMR_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = CMR_k_star, linetype = "dotted") +
  geom_point(aes(x = CMR_k_star, y = CMR_sfk_star), size = 2) +
  geom_point(aes(x = CMR_k_current, y = CMR_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = CMR_last_point$k,
    y = CMR_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = CMR_last_point$k,
    y = CMR_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = CMR_last_point$k,
    y = CMR_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - Cameroon",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(CMR_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

CMR_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    CMR_k_star,
    CMR_k_star,
    CMR_k_current
  ),
  y_coordinate = c(
    CMR_sfk_star,
    CMR_y_star,
    CMR_y_current
  )
)

CMR_ss_points_ft <- CMR_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Cameroon Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

CMR_ss_points_ft
```

### Ghana

```{r}

# ======== Ghana ========

GHA_solow <- pwt_solow %>%
  filter(country == "Ghana")

# Input Variables

GHA_a         <- GHA_solow$a[1]
GHA_s         <- GHA_solow$s[1]
GHA_n         <- GHA_solow$n[1]
GHA_d         <- GHA_solow$d[1]
GHA_A         <- GHA_solow$A[1]
GHA_k_current <- GHA_solow$k[1]
GHA_y_current <- GHA_solow$y[1]

# Steady State

GHA_k_star <- ((GHA_s * GHA_A) / (GHA_n + GHA_d))^(1 / (1 - GHA_a))
GHA_y_star <- GHA_A * GHA_k_star^GHA_a
GHA_sfk_star <- GHA_s * GHA_y_star

# Graph

GHA_solow_df <- data.frame(
  k = seq(0, GHA_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = GHA_A * k^GHA_a,
    sfk = GHA_s * y,
    break_even = (GHA_n + GHA_d) * k
  )

GHA_last_point <- GHA_solow_df %>%
  slice_tail(n = 1)

ggplot(GHA_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = GHA_k_star, linetype = "dotted") +
  geom_point(aes(x = GHA_k_star, y = GHA_sfk_star), size = 2) +
  geom_point(aes(x = GHA_k_current, y = GHA_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = GHA_last_point$k,
    y = GHA_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = GHA_last_point$k,
    y = GHA_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = GHA_last_point$k,
    y = GHA_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - Ghana",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(GHA_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

GHA_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    GHA_k_star,
    GHA_k_star,
    GHA_k_current
  ),
  y_coordinate = c(
    GHA_sfk_star,
    GHA_y_star,
    GHA_y_current
  )
)

GHA_ss_points_ft <- GHA_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Ghana Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

GHA_ss_points_ft
```

### Liberia

```{r}

# ======== Liberia ========

LIB_solow <- pwt_solow %>%
  filter(country == "Liberia")

# Input Variables

LIB_a         <- LIB_solow$a[1]
LIB_s         <- LIB_solow$s[1]
LIB_n         <- LIB_solow$n[1]
LIB_d         <- LIB_solow$d[1]
LIB_A         <- LIB_solow$A[1]
LIB_k_current <- LIB_solow$k[1]
LIB_y_current <- LIB_solow$y[1]

# Steady State

LIB_k_star <- ((LIB_s * LIB_A) / (LIB_n + LIB_d))^(1 / (1 - LIB_a))
LIB_y_star <- LIB_A * LIB_k_star^LIB_a
LIB_sfk_star <- LIB_s * LIB_y_star

# Graph

LIB_solow_df <- data.frame(
  k = seq(0, LIB_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = LIB_A * k^LIB_a,
    sfk = LIB_s * y,
    break_even = (LIB_n + LIB_d) * k
  )

LIB_last_point <- LIB_solow_df %>%
  slice_tail(n = 1)

ggplot(LIB_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = LIB_k_star, linetype = "dotted") +
  geom_point(aes(x = LIB_k_star, y = LIB_sfk_star), size = 2) +
  geom_point(aes(x = LIB_k_current, y = LIB_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = LIB_last_point$k,
    y = LIB_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = LIB_last_point$k,
    y = LIB_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = LIB_last_point$k,
    y = LIB_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - Liberia",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(LIB_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

LIB_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    LIB_k_star,
    LIB_k_star,
    LIB_k_current
  ),
  y_coordinate = c(
    LIB_sfk_star,
    LIB_y_star,
    LIB_y_current
  )
)

LIB_ss_points_ft <- LIB_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Liberia Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

LIB_ss_points_ft
```

### Nigeria

```{r}

# ======== Nigeria ========

NGA_solow <- pwt_solow %>%
  filter(country == "Nigeria")

# Input Variables

NGA_a         <- NGA_solow$a[1]
NGA_s         <- NGA_solow$s[1]
NGA_n         <- NGA_solow$n[1]
NGA_d         <- NGA_solow$d[1]
NGA_A         <- NGA_solow$A[1]
NGA_k_current <- NGA_solow$k[1]
NGA_y_current <- NGA_solow$y[1]

# Steady State

NGA_k_star <- ((NGA_s * NGA_A) / (NGA_n + NGA_d))^(1 / (1 - NGA_a))
NGA_y_star <- NGA_A * NGA_k_star^NGA_a
NGA_sfk_star <- NGA_s * NGA_y_star

# Graph

NGA_solow_df <- data.frame(
  k = seq(0, NGA_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = NGA_A * k^NGA_a,
    sfk = NGA_s * y,
    break_even = (NGA_n + NGA_d) * k
  )

NGA_last_point <- NGA_solow_df %>%
  slice_tail(n = 1)

ggplot(NGA_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = NGA_k_star, linetype = "dotted") +
  geom_point(aes(x = NGA_k_star, y = NGA_sfk_star), size = 2) +
  geom_point(aes(x = NGA_k_current, y = NGA_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = NGA_last_point$k,
    y = NGA_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = NGA_last_point$k,
    y = NGA_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = NGA_last_point$k,
    y = NGA_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - Nigeria",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(NGA_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

NGA_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    NGA_k_star,
    NGA_k_star,
    NGA_k_current
  ),
  y_coordinate = c(
    NGA_sfk_star,
    NGA_y_star,
    NGA_y_current
  )
)

NGA_ss_points_ft <- NGA_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Nigeria Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

NGA_ss_points_ft
```

### Senegal

```{r}

# ======== Senegal ========

SEN_solow <- pwt_solow %>%
  filter(country == "Senegal")

# Input Variables

SEN_a         <- SEN_solow$a[1]
SEN_s         <- SEN_solow$s[1]
SEN_n         <- SEN_solow$n[1]
SEN_d         <- SEN_solow$d[1]
SEN_A         <- SEN_solow$A[1]
SEN_k_current <- SEN_solow$k[1]
SEN_y_current <- SEN_solow$y[1]

# Steady State

SEN_k_star <- ((SEN_s * SEN_A) / (SEN_n + SEN_d))^(1 / (1 - SEN_a))
SEN_y_star <- SEN_A * SEN_k_star^SEN_a
SEN_sfk_star <- SEN_s * SEN_y_star

# Graph

SEN_solow_df <- data.frame(
  k = seq(0, SEN_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = SEN_A * k^SEN_a,
    sfk = SEN_s * y,
    break_even = (SEN_n + SEN_d) * k
  )

SEN_last_point <- SEN_solow_df %>%
  slice_tail(n = 1)

ggplot(SEN_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = SEN_k_star, linetype = "dotted") +
  geom_point(aes(x = SEN_k_star, y = SEN_sfk_star), size = 2) +
  geom_point(aes(x = SEN_k_current, y = SEN_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = SEN_last_point$k,
    y = SEN_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = SEN_last_point$k,
    y = SEN_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = SEN_last_point$k,
    y = SEN_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - Senegal",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(SEN_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

SEN_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    SEN_k_star,
    SEN_k_star,
    SEN_k_current
  ),
  y_coordinate = c(
    SEN_sfk_star,
    SEN_y_star,
    SEN_y_current
  )
)

SEN_ss_points_ft <- SEN_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Senegal Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

SEN_ss_points_ft
```

### Sierra Leone

```{r}

# ======== Sierra Leone ========

SIR_solow <- pwt_solow %>%
  filter(country == "Sierra Leone")

# Input Variables

SIR_a         <- SIR_solow$a[1]
SIR_s         <- SIR_solow$s[1]
SIR_n         <- SIR_solow$n[1]
SIR_d         <- SIR_solow$d[1]
SIR_A         <- SIR_solow$A[1]
SIR_k_current <- SIR_solow$k[1]
SIR_y_current <- SIR_solow$y[1]

# Steady State

SIR_k_star <- ((SIR_s * SIR_A) / (SIR_n + SIR_d))^(1 / (1 - SIR_a))
SIR_y_star <- SIR_A * SIR_k_star^SIR_a
SIR_sfk_star <- SIR_s * SIR_y_star

# Graph

SIR_solow_df <- data.frame(
  k = seq(0, SIR_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = SIR_A * k^SIR_a,
    sfk = SIR_s * y,
    break_even = (SIR_n + SIR_d) * k
  )

SIR_last_point <- SIR_solow_df %>%
  slice_tail(n = 1)

ggplot(SIR_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = SIR_k_star, linetype = "dotted") +
  geom_point(aes(x = SIR_k_star, y = SIR_sfk_star), size = 2) +
  geom_point(aes(x = SIR_k_current, y = SIR_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = SIR_last_point$k,
    y = SIR_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = SIR_last_point$k,
    y = SIR_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = SIR_last_point$k,
    y = SIR_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - Sierra Leone",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(SIR_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

SIR_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    SIR_k_star,
    SIR_k_star,
    SIR_k_current
  ),
  y_coordinate = c(
    SIR_sfk_star,
    SIR_y_star,
    SIR_y_current
  )
)

SIR_ss_points_ft <- SIR_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Sierra Leone Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

SIR_ss_points_ft

```

### Togo

```{r}

# ======== Togo ========

TOG_solow <- pwt_solow %>%
  filter(country == "Togo")

# Input Variables

TOG_a         <- TOG_solow$a[1]
TOG_s         <- TOG_solow$s[1]
TOG_n         <- TOG_solow$n[1]
TOG_d         <- TOG_solow$d[1]
TOG_A         <- TOG_solow$A[1]
TOG_k_current <- TOG_solow$k[1]
TOG_y_current <- TOG_solow$y[1]

# Steady State

TOG_k_star <- ((TOG_s * TOG_A) / (TOG_n + TOG_d))^(1 / (1 - TOG_a))
TOG_y_star <- TOG_A * TOG_k_star^TOG_a
TOG_sfk_star <- TOG_s * TOG_y_star

# Graph

TOG_solow_df <- data.frame(
  k = seq(0, TOG_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = TOG_A * k^TOG_a,
    sfk = TOG_s * y,
    break_even = (TOG_n + TOG_d) * k
  )

TOG_last_point <- TOG_solow_df %>%
  slice_tail(n = 1)

ggplot(TOG_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = TOG_k_star, linetype = "dotted") +
  geom_point(aes(x = TOG_k_star, y = TOG_sfk_star), size = 2) +
  geom_point(aes(x = TOG_k_current, y = TOG_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = TOG_last_point$k,
    y = TOG_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = TOG_last_point$k,
    y = TOG_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = TOG_last_point$k,
    y = TOG_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - Togo",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(TOG_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

TOG_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    TOG_k_star,
    TOG_k_star,
    TOG_k_current
  ),
  y_coordinate = c(
    TOG_sfk_star,
    TOG_y_star,
    TOG_y_current
  )
)

TOG_ss_points_ft <- TOG_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "Togo Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

TOG_ss_points_ft
```

### United States

```{r}

# ======== United States ========

USA_solow <- pwt_solow %>%
  filter(country == "United States")

# Input Variables

USA_a         <- USA_solow$a[1]
USA_s         <- USA_solow$s[1]
USA_n         <- USA_solow$n[1]
USA_d         <- USA_solow$d[1]
USA_A         <- USA_solow$A[1]
USA_k_current <- USA_solow$k[1]
USA_y_current <- USA_solow$y[1]

# Steady State

USA_k_star <- ((USA_s * USA_A) / (USA_n + USA_d))^(1 / (1 - USA_a))
USA_y_star <- USA_A * USA_k_star^USA_a
USA_sfk_star <- USA_s * USA_y_star

# Graph

USA_solow_df <- data.frame(
  k = seq(0, USA_k_current * 2, length.out = 500)
) %>%
  mutate(
    y = USA_A * k^USA_a,
    sfk = USA_s * y,
    break_even = (USA_n + USA_d) * k
  )

USA_last_point <- USA_solow_df %>%
  slice_tail(n = 1)

ggplot(USA_solow_df, aes(x = k)) +
  geom_line(aes(y = y), linewidth = 1, color = "black") +
  geom_line(aes(y = sfk), linewidth = 1.2, color = "darkgreen") +
  geom_line(aes(y = break_even), linewidth = 1.2, color = "red") +
  geom_vline(xintercept = USA_k_star, linetype = "dotted") +
  geom_point(aes(x = USA_k_star, y = USA_sfk_star), size = 2) +
  geom_point(aes(x = USA_k_current, y = USA_y_current), size = 2.5, color = "black") +
  annotate(
    "text",
    x = USA_last_point$k,
    y = USA_last_point$y * 1.03,
    label = "y = f(k)",
    hjust = 0
  ) +
  annotate(
    "text",
    x = USA_last_point$k,
    y = USA_last_point$sfk * 1.03,
    label = "s f(k)",
    color = "darkgreen",
    hjust = 0
  ) +
  annotate(
    "text",
    x = USA_last_point$k,
    y = USA_last_point$break_even * 1.03,
    label = "(n + d)k",
    color = "red",
    hjust = 0
  ) +
  labs(
    title = "Solow Growth Model - United States",
    x = "Capital per Worker (k)",
    y = "Output / Investment per Worker"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    axis.ticks = element_line(color = "black"),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  coord_cartesian(
    xlim = c(0, max(USA_solow_df$k) * 1.15),
    clip = "off"
  )

# Flextable

USA_ss_points <- tibble(
  Point = c(
    "Steady-State Intersection",
    "Steady-State Production",
    "Current Production"
  ),
  x_coordinate = c(
    USA_k_star,
    USA_k_star,
    USA_k_current
  ),
  y_coordinate = c(
    USA_sfk_star,
    USA_y_star,
    USA_y_current
  )
)

USA_ss_points_ft <- USA_ss_points %>%
  mutate(
    x_coordinate = round(x_coordinate, 2),
    y_coordinate = round(y_coordinate, 2)
  ) %>%
  flextable() %>%
  add_header_row(
    values = "United States Solow Model Key Coordinates",
    colwidths = 3
  ) %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  bold(part = "header") %>%
  theme_box() %>%
  align(align = "center", part = "all") %>%
  valign(valign = "center", part = "all") %>%
  autofit()

USA_ss_points_ft
```

### References

Feenstra, Robert C., Robert Inklaar and Marcel P. Timmer (2015), "The Next Generation of the Penn World Table" American Economic Review, 105(10), 3150-3182, available for download at www.ggdc.net/pwt
